---
title: "individual2"
author: "Tyler Kruzan"
date: "2/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Lab 2
```{r, echo=FALSE}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
```

1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
```{r}
hist(choco$Rating, main ="Distribution of Chocolate Ratings", xlab = "Rating (1-5)")
``` 

As can see can see the majority of the ratings are in between 2.5 & 3.5. Below is a boxplot of the ratings, which exemplifies the outliers which are a rating of 5.0 and below around 2.25
```{r}
summary(choco$Rating)
boxplot(choco$Rating, ylab= "Rating", main= "Chocolate Ratings Boxplot")
```

2. Do ratings depend on the cacao percentage of a chocolate bar?
Below is a graph comparing the chocolate ratings and their respecive cocoa percentages. From the graph you can see the outliers of ratings & cocoa percentages and interperet the correlation between the two.

```{r}
plot(choco$Rating, choco$Cocoa.Pct, main="Chocolate Ratings vs. Cocoa %", xlab = "Chocolate Rating", ylab = "Cocoa %")
```

For the most part, the chocolates with a cocoa % between 50%-90% there isn't a strong corellation with Rating. When you see outlier ratings the only chocolate with a 5 star rating had a cocoa % of about 70% and the poorly rated chocolates varied from 70% to 100% cocoa.
